### 2016-04-07 talk/ecoop2009/jitgen.tex
(fijal, cfbolz) work on blog post

There are cases in which having a green variable is essential for generating
good code, but it is not possible to use the \texttt{concrete} due to an
unsatisfiable dependency: Section~\ref{sec:promotion} introduces
\emph{promotion}, the novel technique that makes possible to solve this
problem.

>>>>

There are cases in which having a green variable is essential for generating
good code, but it is not possible to use the \texttt{concrete} hint due to an
unsatisfiable dependency: Section~\ref{sec:promotion} introduces
\emph{promotion}, the novel technique that makes possible to solve this
problem.
